Think deep for reef resilience

### 2025-08-17 paper/paper_draft.qmd
Expand on PDP figure caption

Reefs have the greatest probability of being clustered into Low if shallow, and High at
greater depths, with medium cluster reefs exhibiting a lower, and stable, variation in
assignment probability across depth ranges [@fig-ts-cluster-pdp, Panel B]. A large increase
in the probability of a reef being categorised as High can be seen between 10 and 12 meters
depth. This is at the edge of what is feasible with current technologies and restoration
approaches **\[TI: Citation here\]**, but indicates a depth range that could be adopted to
maximise longevity and benefits of, for example, coral seeding activities. With regard to
DHWs, assignment probability is roughly equal across the three categories up to 6 DHW. A
sharp delineation can be seen \> 6 DHW when comparing High with other categories, with lower
assignment probability (\~25%) compared to Medium and Low (\~40%).

@@

**\[BG: Will add either predictor distributions to these sub plots, or just in a general
variable distribution plot in the supplementary material.\]**

![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
Dependence Plots for reef characteristics of interest indicating the probability of a reef
being classified to one of the three categories (Panel B). Partial Dependence Plots for
bioregions were excluded as they were found to be
uninformative.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp
fig-align="center" width="9.2cm"}

>>>>

Reefs have the greatest probability of being clustered into Low if shallow, and High at
greater depths, with medium cluster reefs exhibiting a lower, and stable, variation in
assignment probability across depth ranges [@fig-ts-cluster-pdp, Panel B]. A large increase
in the probability of a reef being categorised as High can be seen between 10 and 12 meters
depth. This is at the edge of what is feasible with current technologies and restoration
approaches **\[TI: Citation here\]**, but indicates a depth range that could be adopted to
maximise longevity and benefits of, for example, coral seeding activities. With regard to
DHWs, assignment probability is roughly equal across the three categories up to 6 DHW. A
sharp delineation can be seen \> 6 DHW when comparing High with other categories, with lower
assignment probability (\~25%) compared to Medium and Low (\~40%) [@fig-ts-cluster-pdp,
Panel B].

@@

![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
Dependence Plots (PDPs) for reef characteristics of interest indicating the probability of a
reef being classified to one of the three categories (Panel B). Partial Dependence Plots for
bioregions were excluded as they were found to be uninformative. PDPs indicate the
probability of a reef from the test dataset being clustered into each cluster category
depending on the predictor value on the x axis, when adjusted for values of other
predictors. Green, orange and blue lines indicate cluster assignment probability for Low,
Medium and High clusters respectively. Transparent grey points above probability lines
represent the predictor values present in the test dataset, providing a rough indication of
predcitor value distribution across
reefs.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp fig-align="center"
width="14.82cm"}
